WrapITK: Enhanced languages support\\ for the Insight Toolkit

### 2006-08-28 article/Article.tex
add a note about solaris linker bug
darcs-hash:20060810143422-2fc9d-c88b8ea6fb5e954cbf807f0c6dfc1fa655fefa51.gz
fix Benoit's afffiliation
darcs-hash:20060828132449-2fc9d-03457b50c6586f216c7b9728c8edf606f30aaf9a.gz

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{Ga\"etan Lehmann{$^1$}{\small{,}} Zachary Pincus{$^2$} {\small{and}} Benoit Regrain{$^3$}}
\authoraddress{{$^1$}INRA, UMR 1198; ENVA; CNRS, FRE 2857, Biologie du D\'eveloppement et 
Reproduction, Jouy en Josas, F-78350, France\\
{$^2$}Program in Biomedical Informatics and Department of Biochemistry, Stanford University School of Medicine, Stanford, California\\
{$^3$}CREATIS, CNRS UMR 5515, 69621 Villeurbanne, France}

@@

>>>>

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{Ga\"etan Lehmann{$^1$}{\small{,}} Zachary Pincus{$^2$} {\small{and}} Benoit Regrain{$^3$}}
\authoraddress{{$^1$}INRA, UMR 1198; ENVA; CNRS, FRE 2857, Biologie du D\'eveloppement et 
Reproduction, Jouy en Josas, F-78350, France\\
{$^2$}Program in Biomedical Informatics and Department of Biochemistry, Stanford University School of Medicine, Stanford, California\\
{$^3$}CREATIS, CNRS UMR 5515, Inserm U630, Univ. Lyon1, INSA Lyon, 69621 Villeurbanne, France}

@@

Solaris users may have so problem to build WrapITK if they have a recent version of
gcc. A workaround can be activated in WrapITK to fix that problem, by passing the
option \verb$-DSUNOS_STDCXX_FIX:BOOL=ON$ to \verb$cmake$ or \verb$ccmake$.
